% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{fontspec}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Fábio Gabriel de Magalhães} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Sydney, New South Wales, Australia} % Your address
\moveleft.5\hoffset\centerline{+61 0481 850 475}
\moveleft.5\hoffset\centerline{fmagalhaes@gmail.com}
\moveleft.5\hoffset\centerline{GitHub: https://github.com/fabiogm}
\moveleft.5\hoffset\centerline{LinkedIn: https://www.linkedin.com/in/fmagalhaes/}

\begin{resume}

\section{ABOUT} Software engineer with over ten years of experience. Worked on projects ranging from greenfield applications to large 
	legacy systems, across diverse industries like retail, healthcare and banking. Quantitative background and interest in data science.

\section{COMPUTER \\ SKILLS} {\sl Programming Languages:} Java, Python, Ruby, Javascript, SQL, R, C, C++\\
    {\sl Databases, Data Stores \& Tools:} PostgreSQL, DynamoDB, Hive, HBase\\
    {\sl Cloud Platforms:} Amazon Web Services, Pivotal Cloud Foundry\\
		{\sl Methodologies:} Agile software development, lean practices, test-driven development, behavior-driven development
 
\section{EXPERIENCE}{\sl Software Engineer} \hfill 2018-Present\\
	Atlassian
	\begin{itemize}
	  \item implementing new user sign-up flows for Atlassian cloud products.
	  \item worked on the initiative to support European General Data Protection Regulation in Jira Cloud.
         \end{itemize}

	{\sl Consultant Developer} \hfill 2014-2018\\
		ThoughtWorks
		\begin{itemize}
      \item The Gap, Inc. (2016 - 2018) - created an ecosystem of applications used by the allocator managers of the brands to allocate products 
        to stores and control product life-cycles across several markets around the world. The web UI presents users with several attributes of each product 
        and helps in the decision making process by presenting sales forecast for products. Event-driven microservices architecture, with Java services 
        communicating via REST APIs and RabbitMQ for asynchronous messaging. Deployed to an on-premises Pivotal Cloud Foundry environment. 
        The allocation UI is an AngularJS Single Page Application.
      \item The Gap, Inc. (2015 - 2016) - developed a large scale order routing system responsible for routing e-commerce orders. The system
        also helps remove stranded inventory from stores, making more products available to online customers and increasing profits. Back end application using Java.
      \item Leading US healthcare improvement company (November 2014 - July 2015) - created a web application for reconciliation and contract revenue forecasting used 
        by contract managers. The system made contract revenue more predictable enabling contract managers to take corrective actions sooner. The system was deployed to 
        Amazon Web Services and was composed of a web application using AngularJS, a backend for frontend application implemented in Java and a predictive model 
        implemented in Python.
      \item Large US online marketing and advertising provider (July - October 2014) - implemented a control panel for advertising campaign managers that aids the 
        creation of more effective campaigns in order to optimize user's marketing budgets. Single Page Application using AngularJS and a backend for frontend 
        implemented in Ruby on Rails.
      \item Large Brazilian retailer (2014) - developed a proof of concept of a business intelligence system including data ingestion, data transformation 
        and stock metrics reporting using Hive in the cloud (Amazon EMR).  Interface with legacy systems using Ruby and Oracle 11g.
		\end{itemize} 
                {\sl Freelance Developer} \hfill 2012-2013
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed websites using Python and Javascript
                \item Developed a small scale CMS using Python running on Google App Engine platform
                \item Developed a prototype for a platform game using Python and PyGame
                \end{itemize}
 
                {\sl Software Engineer} \hfill            2009 - 2011\\
                Tools and Technologies 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Worked in the design and implementation of banking software for ATMs, using C++ (backend),
                       HTML and Javascript(UI). Acted as a contractor for a Brazilian company which is the largest player
                       in the segment of technologies and services for business and electronic transactions.
                 \item Worked in the design, implementation and maintenance of firmware for storage controllers using C. 
                       Also contributed in the design, implementation and maintenance of test infrastructure 
                       using C++ under Unix. Acted as a contractor for a multinational company in a demographically distributed team.
                 \end{itemize} 

                {\sl Software Developer} \hfill        2008 - 2009\\
                Datum TI
                  \begin{itemize}
			  \item Worked in the design, implementation and maintenance of banking software (point of sale automation). 
				  Employed C++ for branch server and Visual Basic for points of sale on a service-oriented architecture over DCOM. 
                   \end{itemize} 

\section{EDUCATION} {\sl Bachelor of Science,} Mathematics \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Universidade Federal do Rio Grande do Sul (UFRGS), Brazil \\ 
                2012-2016

                   {\sl Bachelor of Science,} Computer Science \\
                Universidade do Vale do Rio dos Sinos (Unisinos), Brazil \\
                2006-2010 (Did not graduate)

                   {\sl Technician,} Information Systems \\
                Colégio São Luís, Brazil \\
                2001-2004
	
\section{CONTINUING \\ EDUCATION} Statistical Inference, Practical Machine Learning, Regression Models, Reproducible Research, 
                                    R Programming, Getting and Cleaning Data, The Data Scientist's Toolbox, Exploratory Data Analysis\\
                                    (Courses from John Hopkins University online specialization in Data Science, 2014-2017)\\
                                  Development of ARM7 firmware using C language (2010)

\section{LANGUAGES} Portuguese (Native), English (Full professional proficiency)
 
\end{resume}
\end{document}

