%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov, Fabio Magalhaes
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{customresume}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Fabio Gabriel de Magalhaes}
\address{Porto Alegre \linebreak Rio Grande do Sul, Brazil}
\contacts{+55 51 982161084 \linebreak fmagalhaes@gmail.com}

\begin{document}
	% Print the header
	\makeheader
	% Print the content
	\begin{cvsection}{Employment}
    \begin{cvsubsection}{Software Consultant/Engineer}{ThoughtWorks}{2014 - Present}
      \textit{Gap Inc.}
			\begin{itemize}
				\item Created an ecosystem of applications that enables supply chain managers to control the life-cycle of products and allocate products 
          to stores efficiently and effectively around the world. The system supports the decision-making process by presenting metrics and forecasts. 
				\item Extended an order routing system that fulfills all orders from the company e-commerce. Created configurable options to tune order routing 
          process to remove stranded inventory from certain locations, optimizing profits.
			\end{itemize}
      \vspace{5pt}
      \textit{Leading US Healthcare Improvement Company}
      \begin{itemize}
        \item Created a web-based application for accounting reconciliation and revenue forecasting, enabling contract managers to take corrective actions
          sooner and increase revenue. The forecast service provided highly accurate predictions that required human intervention in less than 2\% of cases.
      \end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Freelance Software Engineer}{}{2012 - 2013}	
			\begin{itemize}
        \item Developed a small scale Content Management System (CMS) using Python running on Google App Engine platform.
				\item Developed prototypes for platform games using Python and PyGame.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Consultant/Engineer}{Tools and Technologies}{2009 - 2011}		
      \textit{Leading Brazilian Electronic Payment Provider}
			\begin{itemize}
        \item Implemented software for Automatic Teller Machines with innovative cash recycling hardware (first to operate in Brazil). 
			\end{itemize}
      \vspace{5pt}
      \textit{Hewlett Packard}
      \begin{itemize}
				\item Extended the firmware for hardware monitoring module of a virtual storage disk array system.
      \end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Consultant/Engineer}{Datum TI}{2008 - 2009}
      Large Government-Owned Brazilian Bank
			\begin{itemize}
        \item Extended banking systems used by bank tellers to perform all transactions.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Brazil}{Federal University of Rio Grande do Sul}{2012 - 2016}
			\begin{itemize}
				\item B.S.c. in Applied Mathematics, December 2016.
				\item Relevant coursework: Calculus; Advanced Calculus; Ordinary Differential Equations; Partial Differential Equations; Statistics; 
          Computational Statistics, Combinatorial Optimization.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Brazil}{Unisinos}{2006 - May 2010}
			\begin{itemize}
        \item B.S.c. in Computer Science (not graduated).
        \item Relevant coursework: Programming in Java; Programming in C++; Data Structures; Computational Complexity; Computational Theory; Information Theory.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages, Technologies, Methodologies and Other}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
        \item Java (Spring, Spring Boot); Python; Ruby (Ruby on Rails); C; JavaScript (Node.js); R; C++; SQL
        \item PostgreSQL; MongoDB; Hive; HBase;
        \item Microservices, REST APIs; Event-driven Architectures; RabbitMQ; Pivotal Cloud Foundry; Amazon Web Services
        \item Agile software development; lean practices; test-driven development; behavior-driven development
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
